Towards a Verified Tableau Prover for a Quantifier-Free Fragment of Set Theory

### 2023-03-06 paper/CADE/paper.tex
paper: AND verify

Since we are only interested in the level of a term, we can encode all constraints into the theory consisting of $0$, the successor function \lstinline!S!, and equality (but no disequality).
Note that constraints of the form \lstinline!l $\neq$ 0! can be replaced by \lstinline!l $=$ S i! with \lstinline!i! being a fresh variable.
A solver for this theory is straightforward to implement;
nevertheless, we have to be careful that it computes the minimum assignment $\Gamma$ from variables to levels that fulfils the constraints. 
This is to guarantee that a set term \lstinline!t! is not an urelement \textbf{iff} \lstinline!$\Gamma$ t $>$ 0!.
Conversely, all terms \lstinline!s! with \lstinline!$\Gamma$ s $=$ 0! are urelements.

>>>>

Since we are only interested in the level of a term, we can encode all constraints into the theory consisting of $0$, the successor function \lstinline!S!, and equality (but no disequality).
Note that constraints of the form \lstinline!l $\neq$ 0! can be replaced by \lstinline!l $=$ S i! with \lstinline!i! being a fresh variable.
A solver for this theory is straightforward to implement and verify;
nevertheless, we have to be careful that it computes the minimum assignment $\Gamma$ from variables to levels that fulfils the constraints. 
This is to guarantee that a set term \lstinline!t! is not an urelement \textbf{iff} \lstinline!$\Gamma$ t $>$ 0!.
Conversely, all terms \lstinline!s! with \lstinline!$\Gamma$ s $=$ 0! are urelements.
